Hydras \& Co.\\ Formalized mathematics in \coq for inspiration and entertainment

### 2021-11-16 doc/hydras.tex
add a link to JFLA's paper
add a link to JFLA; still have to write a small text
Update doc/hydras.tex
Co-authored-by: Karl Palmskog <palmskog@gmail.com>

\SetWatermarkLightness{0.8}
\definecolor{lightorange}{rgb}{1,0.9,0.9}
\SetWatermarkScale{0.35}
\SetWatermarkText{Work in Progress}
\SetWatermarkColor{lightorange}

@@

\title{Hydras, Ordinals \& Co.\\ A library in Coq of entertaining formal mathematics}
%\pagestyle{fancy}
%\fancyhead{Hydras, Ordinals, \& Co.}
\makeindex{coq}
\makeindex{maths}
\makeindex{hydras}
\makeindex{additions}
\makeindex{primrec}
\begin{document}
\maketitle

@@

%%%%% ICI

\subsection{Documenting theories with \alectr}

>>>>

\SetWatermarkLightness{0.8}
\definecolor{lightorange}{rgb}{1,0.9,0.9}
\SetWatermarkScale{0.35}
\SetWatermarkText{Work Continuously in Progress}
\SetWatermarkColor{lightorange}

@@

\title{Hydras \& Co.\\ Formalized mathematics in \coq for inspiration and entertainment}
%\pagestyle{fancy}
%\fancyhead{Hydras, Ordinals, \& Co.}
\makeindex{coq}
\makeindex{maths}
\makeindex{hydras}
\makeindex{additions}
\makeindex{primrec}
\begin{document}
\maketitle

@@

 \subsection{Developing and maintaining the \coq code and documentation}

 \textbf{TODO} introductory text and link to \cite{jfla2022}

 \subsubsection{Continuous Integration and Continuous Delivery}

 \textbf{TODO}

\subsubsection{Documenting theories with \alectr}
